\newcommand{\LineComment}[1]{\Statex \hfill\textit{#1}}
\vspace{-0.15in}
\section{Overview}
In serverless computing, a cloud provider provides the necessary resources for a task and the user specifies the code to execute the task.
Serverless computing tasks tend to be event driven and stateless.
This model benefits the user as users only need to pay for the resources used.
The model also benefits the cloud provider as they only need to provide the resources needed by the user, thus allowing them to save resouces.\\
\newline
Proteins consists of chains of amino acids.
A segment of the chain is called a peptide.
The composition of peptides are analyzed using mass spectrometry and stored in plots call spectra.
Each spectrum contains the m/z (charged mass) of pieces of the peptide correlating to the amino acid composition of the peptide.
Comet is a piece of software that correlates these experimental spectra datasets with theoretical datasets generated using FASTA databases.
The largest FASTA database is the database containing human proteins.
This database contains 750 thousand entries.
An entry in the database is a match if the protein contains the peptide.
However proteins can have modifications.
An n-modification means n of the amino acids in a protein differ from the base protein.\\
\newline
Manually scaling servers to handle all modifications is a challenge and usually researchers resort to only searching a subset of the database.
This means the database may not contain the best match.
Another problem in the proteomics community is researchers want an easy way for people to add new entries to a shared database.
Serverless coputing offers a way for the proteomics community to cheaply and automatically scale these database and a potential way to share data in the community.
